Actuator line modeling of vertical-axis turbines

### 2018-05-05 paper.tex
Address reviewer 3 comments

Before the dynamic stall subroutine is executed, the static profile data for
each element is interpolated linearly based on local chord Reynolds number. The
profile data characteristics---static stall angle, zero-lift drag coefficient,
and separation point curve fit parameters---are then recomputed each time step
such that the effects of Reynolds number on the static data are included.

@@

NREL has developed and released an actuator line modeling library,
SOWFA~\cite{Churchfield2014b}, for simulating horizontal-axis wind turbine
arrays using the OpenFOAM finite volume CFD library. OpenFOAM is free,
open-source, widely used throughout industry and academia, and has grown a very
active support community around itself. Though SOWFA is also open-source, its
mostly procedural style would have required significant effort and duplicate
code to adapt for cross-flow turbines. Thus, a new and more general ALM library
was developed from the ground up that could model both cross- and axial-flow
turbines, as well as standalone actuator lines. The actuator line model
developed here, dubbed turbinesFoam \cite{Bachant2018-turbinesFoam-v0.0.8}, was
also written as an extension library for OpenFOAM (v5.0), using its
\texttt{fvOptions} framework for adding source terms to equations at runtime.
This implementation allows the CFT-ALM to be added to many of the standard
solvers included in OpenFOAM without modification, i.e., it can be readily used
with RANS or LES, multiphase models (e.g., for simulating the free surface in
MHK installations), and even with heat transfer.

>>>>

Before the dynamic stall subroutine is executed, the static profile data for
each element is interpolated linearly based on local chord Reynolds number,
which is calculated based on the detected inflow velocity for each actuator
line element and the simulation's kinematic viscosity. The
profile data characteristics---static stall angle, zero-lift drag coefficient,
and separation point curve fit parameters---are then recomputed each time step
such that the effects of Reynolds number on the static data are included.

@@

NREL has developed and released an actuator line modeling library,
SOWFA~\cite{Churchfield2014b}, for simulating horizontal-axis wind turbine
arrays using the OpenFOAM finite volume CFD library. OpenFOAM is free,
open-source, widely used throughout industry and academia, and has grown a very
active support community around itself. Though SOWFA is also open-source, its
architecture is focused on simulating horizontal-axis wind turbine arrays
in the atmospheric boundary layer and would have required significant effort to
adapt for cross-flow turbines. Thus, a new and more general ALM library
was developed that could model both cross- and axial-flow
turbines, as well as standalone actuator lines. The actuator line model
developed here, turbinesFoam \cite{Bachant2018-turbinesFoam-v0.0.8}, was
also written as an extension library for OpenFOAM (v5.0), using its
\texttt{fvOptions} framework for adding source terms to equations at runtime.
This implementation allows the CFT-ALM to be added to many of the standard
solvers included in OpenFOAM without modification, i.e., it can be readily used
with RANS or LES, multiphase models (e.g., for simulating the free surface in
MHK installations), and even with heat transfer.
